Social Network Analysis: Week 3: Degree and Centrality

### 2022-03-06 docs/3. SNA - Assignments/DRAFT_Week3-Distill-Blog_Degree-and-Centrality.Rmd
3.6.22

@@

    1.  **What do you make of network density and
        centralization measures?\
        **

        +---+---+---+---+
        | A | s | i | P |
        | n | t | g | l |
        | a | a | r | o |
        | l | t | a | t |
        | y | n | p |   |
        | s | e | h |   |
        | i | t |   |   |
        h       | s|    |   |  |
        +====+===+===+===+
        | D | M | 0 | y |
        | y | u | . | e |
        | a | t |   | s |
        | d | u | 0 |   |
      |  yC | a | 1 |  |
        | e n| l | 7 |   |
        | n | : | 9 |   |
        | s | 1 |   |  | 
        |       | u |
  |   |   |           s | A |   |   |
          | | s |1 7| 9  
        |
  | y |   |   |           | | m |s y| m m
        |   |     | |   |
        |
  | e |   |   |           | | t |t r| i c
        |   | r |     | |
        |
  | i |   |   |           | | c |   |   |
        |   | a |   |   |
        |   | l |     | |
        |
  | : |   |   |           | | 6 |   |    
        |   | 7 |     | |
        |
  | 0 |   |   |           | |   |   |   |
 |      |     N |   |   |
        |
  | u |   |   |           | | l |u l| l :
        |   | l |     | |
        |
  | : |   |   |           | | 3 |6 7| 3 0
        |   | 6 |   |   |
        |   | 7 |   |   |
        |   | 3 |     | |
        |
  | 0 |   |   +-----------+-+---+---+---+
        | T | 0 | \ |   |
        | r | : | | |   |
        | C e n s i | 3 | l |   |
        | a | 2 |   |   |
        | d | 1 |       |
|
        C | 6 |   |       |       e | 3 |   |    
        |       | n | 9 |   |   |
     |    s | 1 |   |  | 1 : 7 8   |u |   |   |    
        | s | 1 |   |   |
        | : | : |  |
   |
     | A    | 7 |   | |  \|        |  | 8 |   |    
        |   | \ |  |
   |
     +------| | |   |--+-----------+--+---+---+| \| l \| l \| 9 \| \| \| \| T \|
        0 \| \| \| \|\|\| r \| \| \|\
        \| \| i \| 2 \| \| 2 \| a \| : \| \| \| \|
        d \| 1 \| \| \| \| \|\| \| s \| \| \| \|
        \| \|i\| 6 \| i 4 \|n 7\|\| \| \|

|    \|\| N \| \| \| N
|  \| \| e \| 4 \| 4 e \| \|\| t \| \| \| \| \| w \| \| 3 \| \|\| \| \| oo \| \| \|\| \| \|r\| r \| \| \|
|      \|\| k \| \| \| \| k +---+---+-----+ \| T \|-- \| ( \| y \| \| r \| 3 \| u \| e \| \| i \| 9 \| n \| s \| \| a \| 1 \| d \| \| \| d \| 0 \| i \| \| \| C \| 2 \| r \| \| \| e \| 4 \| e \| \| \| \| cn \| \| \| \| n \| \|\|d g\| ss s t \| \| u \| \| e \| \| \| s \| \| d \| \| \| : \| \| g \| \| \| \|aph r \| t\| \| \| at \| \| \| \| \| \|\|\| \| \| \| p \| \| \| t \| t\| h \| \| \| )a \| \| \| l \| \| \| \| \| n \| \| [ \| \| \| u \| \| 1 \| \| mber \| m \| \| 2 \|

] \| \| b \| \| 3 \| \|\| \|\|\
\| e e 2 \| \| \| r \| \| 1 \|665\| 9 \| 6\| o \|
\| \| \|\
\| f\| \| 6 \| \| riad t \| \| \| a \|a \| 5 \| l
\| \| 9\
\| \| l \|\| \| \| ypes \| \| [ \| f \| [] \| \|
\|\| 16\| o o \| 2 \| \| \| u \| \| ] \| \| \| r
\| \| 1 \| \| \| t \| \| 6 \| \| \| r \| \| 6 \|
\| \| i \| \| 4 \| \| \| a \| \| 8 \| \| \| d \|
\| \| \| \|6 6 6 \| \|\| t \| t \|\
\| y \| \| [ \| \| \| p \| \| 1 \| \| \| e \| \| 1
\| \| \| s \| \| ] \| \| \| \| \|\| \| \|\
\| [\|11]\| 8 \| \| 8 \| \| \| 7 \|\
\| +-\|- \| \| \| \| +-- -+---+---+---+ \| T \| u
\| U \| \| \| r \| n \| n \| \| \| a \| d \| d \|
\| \| n \| i \| i \| \| \| s \| r \| r \| \| \| i
\| e \| \|\
e e \| e \| \| c t c \| t \| i \| t \| t \| \| \|
v \| e \| e \| \| \| i \| d \| d \| \| \| t \|
\|\| \|--\|\| \| y \|\| \| \|\| +---+---+---+L oal
---+ \| L \|L \| \| \| \| o \| \| \| c \| \| \| \|
\| a \| \| \| \| \| \| \|l \| l \| \| \|t \| \| \|
\| r \| \| \|ran s \| \| \| a \| \| a \| n \|\| \|
\| \| \| \| \| \| \| \| i \| \| \| \| \| t \| \|
\| \| \| i \| \| \| \| \| v \| \| \| \| \| i \| \|
\| \| \| t \| \| \| \| \|\| \| \| \| \|\| \| \| \|
: \| \| \| \| \| N \| \| \| \| \| o \| \| \| \| \|
d \| \| \| \| \| e \| \| \| \| \| L \| \| \| \| \|
i \| \| \|\
\| \| \| \|\|\| s s \| s\
&\| Eg\| t \| \| \| \|

    & &  |

& \| \|E\| \| \|\| \| \| g \| \| \| \| \| o \| \|
\| \| \| N \| \| \| \| \| \| \| e \| \| \| w\|ork
\| \| \| \| \| \|\| w \| \| w \| o \| \|\| \| \|
\|\| \| \| r \| r\| \|\
\|k \| \| \| \| +---+---+---+---+ \| I \| n \| \|
\| \| s \| o \| \| \| \| o \| \| \| \| \| l \| \|
\| \| \| a \| \| \| \| \| t \| \| \| \| \| e \|---
\|\|---\| \| \| \| \| s\| \| \| +---+---+---+---+
\| U \| \| n \| \| \| n \| \| u \| \| \| d \| \| m
\| \| \| i \| \| b \| \| \| r \| \| e \| \| \| e
\| \| r \| \| \| c \| \| : \| \| \| t \| \| 1 \|
\| \| e \| \| \| \| \| d \| \| s \| \| \| : \| \|
i \| \| \| \| \| zC \|C \| C \| \|\| \| o \|\| \|
\|\| \| m \| \| : \| \| \| p \| \| 2 \| \| \| o \|
\| 7 \| \| \| n \| \| 4 \| \| \| e \| \| \| \| n
\|\| S \|\|tru\| \| \| \| t \|\| \| S \| \| \| \|
\| t \| \| \| \| \| r \| \| \| \| \| u \| \|274 \|
\| c \| \| c \| \| c \| \|

    |t |   ||t
    |    |        ||

\| \| +- r \|\| \| \| \|\| e \| \| \| \|
+---+---+rec + \| D \| \| i \| 0 \| y \| \| . \| e
\|\| \| r \| \| 0 \| s \| \| e \| \| 1 \| \| \|
6\|7 \| 6 c \| c \|\| \| d \| \| t \| \| 7 \| \|
\|e e \| \| d \| 6 \| \| \| : \| \| 4 \| \| \| \|
\| \| 2 G \| G 2 \| \|\| 2 R\| \|\| \| \| A \| \|
\| \| \| P \| \| \| \| \| H \| \| \| \| \| : \| \|
\| \| \| D \| \| \| \| \| y \| \| \| \| \| a \| \|
\| \| \|\
d \| C \| \| \| \| \| \| \|\| \| C \| \|\
\| \|\| \| e \| \| \| \| \| \|\| \| s \| \| \| \|
\| \| \| \| \| u \|\| \| s \| \| \| \|
+---+---+---+---+ \| D \| \| \| y \| \| i \| \| \|
e \| \| r \| \| \| s \| \| e \| \| \| \| \| \| \|
c \| \|cy\| cs \|\| \| t \| \| \| t \|\
\| \| \| \| d \| \| \| \| \| : \| \| \| \| \| D \|
\| \| \| \| \| \| \|ee \| e\| \| g \| \| \| \| \|
\| \| r \| \| e \| \| \| \| \| e \| \| \| \| \| C
\| \| \| \| \| e \| \| \| \| \| n \| \| \| \| \| t
\| \| \| \| \| r \| \| \| \| \| a \| \| \| \| \| l
\| \| \| \| \| i \| \| \| \| \| \| \| --- \| t \|
\| \| \| y \| \| \|\| \| +---+---+rec + \| D \| \|
i \| \| y \| \| \| e \|\| \| r \| \| \| s \| \| e
\| \| \| \| \| \| \| c \| \|cy\| cs \|\| t \| \|
\| \| e\
\| \| \| \| d \| \| \| \| \| : \| \| \| \| \| B \|
\| \| \| \| e \| \| \| \| \| t \| \| \| \|

     w |       | | |

\| \|\| \| \| \| \| e \| \| e \| \| \| \| \| n \|
\| \| \| \| n \| \| \| \| \| e \| \| \| \|

     s |       ||  |

\| s \| \| \|\| \| \| C \| \| \| \| \| e \| \| \|
\| \| n \| \| \| \| \| t \| \| \| \| \| \| \| \|\|
rr \| \| \| a \| \| \| \| \| l \| \| \| \| \| i \|
\| \| \| \| \|\| t +-\| --\|-\| \| yy \|\| \|+---
+--+ ----+ --+---+ \| D \| \| y \| \| \| e \| \|
\| r \| \| \| s \| \| e \| \| \| \| \| c \| \| \|
y\| s \| \| \| tedt \| \| \| e \| \|\|\| \|\| \|
\| \| \| \| d \|\
d \| : \| \| \| \| \| E \| \| \| \| \| i \| \| \|
\| \| g \| \| \| \| \| e \| \| \|\| \| \|\| n\| \|
\| \| \| \| v \| \| \| \| \| e \| \| \| \| \| c \|
\| \| \| \| t \| \| \| \|

       o |   C||e |n||

\| \| \| \|\| r \| \| C \| \| \| \| \| e \| \| \|
\| \| n \| \| \| \| \| t \| \| \| \| \| r \| \| \|
\| \| \| a \|\| \|\| \| \| \| \| \| l \| \| \|
\|\| i \| i \| \|t + \|\|\| \|\|\| \| y \| \| \|
\| +---+---+---+---+ \| D \| \| \| \| \| i \| \|
\| \| \| r \| \| \| \| \| \| e \| e\| \| \| \| c
\| \| \|\| \| t \| \| \| \| \| e \| \| \| \| \| d
\| \| \| \| \| : \| \| \| \| \| B \| \| \| \| \| o
\| \| \| \| \| n \| \| \| \| \| a \| \| \| \| \| c
\| \| \| \| \| i \| \| \| \| \| c \| \| \| \| \| h
\| \| \| \| \| C \| \| \| \| \| e \| \| \| \| \| n
\| \| \| \| \| t \| \| \|\| \| \|\| r\| \| \| \|
\| \| a \| \| \| \| \| l \| \| \| \| \| i \| \| \|
\| \| t \| \| \| \|

       y |    ||  | ||
          | 
          |   |   |

} +---+---+---+ \| ------+ +--+ \|\| D \| \|\| i
\| \| \|\| \| \| \| r \| \| \| \| \| \| \| \|\| e
\| \| \| \| \| \| c \|c \|\| c \| \| \|t \| k \|t
\| t \| \| \| \|e \| \| \| \| \| \| \| \| \| \|\|:
\| \| \| \| \| P \| \| \| \| \| \| \| \|\
a \| \| g \|\| \| \| \| \| \| e \| \| \| \| \| R
\| \| \| \| \|a

          | a |   || a||  |

| \| n\| n\| \|n \| \| \| \| \|----- --+ \|

-

    -   ++ + +-+---+ \|+- \| \| +-+ +> Dist+ill+
        \| \| + is+ a publ+ic\| \| \|
        +---+---+---+---+

>>>>

Smuggler's Bay Drink Recipe Book Index

:   Is an edge-list with one edge attribute:

    Vertices:

    -   Drink Name

    -   Drink Ingredient

    Edge Attribute:

    -   Drink Ingredient Type

Network Description

:   Nodes:

    Edges:

    Ties: Are a connection between Drink Names and
    Drink Ingredients. The network is undirected
    and unweighted. Undirected: because the
    relationship between Drink Names and Drink
    Ingredients lacks any sort of power dynamic.
    Edge weights could be added by including the
    amount of each ingredient required for each
    drink recipe.

    -   Statnet: number, directed, unweighted

    -   igraph: number, udirected, unweighted

    Smuggler's Bay Edglist is long but
    uncomplicated: which means there are few ways
    to subset data to help answer our research
    question: ***what sort of relationships exist
    between the components ?*** Which makes Drink
    Ingredient Type edge attribute very useful.

- Whether or not there are edge attributes

that might be used to:

- subset data, or

- stack multiple networks.

@@

    1.  **What do you make of network density and
        centralization measures?**
